Landau quantization of nearly degenerate bands

### 2018-10-01 paper.tex
Updates from ShareLaTeX

Deviating from the adiabatic limit, we deduce from \q{c2breakdowndgncondition} that  $\A{=}I$ remains attainable by varying $B$, but $\A{=}{-}I$ is unattainable because $\tau{<}1$; this is consistent with the codimension analysis of \q{proprashba}. The conditions $\A{=}I$ and $\rho{>}0$ are interpreted as the destructive interference of  two, single-tunneling Feynman path (cf. Fig. \ref{fig:Cn-breakdown}(d)). Concurrently, there is constructive interference of the Feynman loops involving zero and two tunneling events (cf. Fig. \ref{fig:Cn-breakdown}(e)). The differential phase between outer and inner zero-tunneling (band-conserving) loops is simply 0 (mod $2\pi$), hence Landau levels are quasidegenerate. Such quasidegeneracies recur as $\Delta$ advances by $2\pi$, corresponding to a periodicity in $l^2$ of $4\pi/\delta S$ (or two flux quanta). This periodicity is not affected by the additional phase $2\bar{\phi}$ in $\Delta$, because $\bar{\phi}$ varies on the scale  $2\pi/S_{\sma{\square}}$,\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary  $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$ [cf.\  Fig.\ 10 in 100page]. Moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$.[AALG]} which is much larger than $4\pi/\delta S$. To recapitulate, half the Landau-level quasi-crossings (over the $B$ axis) are destabilized  by tunneling; the robustness of the other half relies on $\mathfrak{c}_2$ symmetry. There exists a complementary argument for the existence of Landau-level quasi-crossings in the Klein-tunneling limit $(\tau{=}0)$: the two independent orbits are related by $\mathfrak{c}_2$ symmetry, leading to exactly-degenerate Landau levels.

@@

For our last illustration, we consider a II-Dirac model with $\mathfrak{c}_3$  symmetry, as   illustrated in Fig. \ref{fig:Cn-breakdown}(b). In the adiabatic regime ($\tau{\approx}1$), Landau-level quasidegeneracies occur with a periodicity of one flux quantum; however, in the Klein-tunneling regime ($\tau{\approx}0$), there exists only one dominant orbit shaped like a three-fold-symmetric trefoil knot --  all Landau levels are nondegenerate with spacing determined by the effective mass of the trefoil; this property generalizes to $\mathfrak{c}_N$-symmetric II-Dirac models with odd $N$.

>>>>

Deviating from the adiabatic limit, we deduce from \q{c2breakdowndgncondition} that  $\A{=}I$ remains attainable by varying $B$, but $\A{=}{-}I$ is unattainable because $\tau{<}1$; this is consistent with the codimension analysis of \q{proprashba}. The conditions $\A{=}I$ and $\rho{>}0$ are interpreted as the destructive interference of  two, single-tunneling Feynman path (cf. Fig. \ref{fig:Cn-breakdown}(d)). Concurrently, there is constructive interference of the Feynman loops involving zero and two tunneling events (cf. Fig. \ref{fig:Cn-breakdown}(e)). The differential phase between outer and inner zero-tunneling (band-conserving) loops is simply 0 (mod $2\pi$), hence Landau levels are quasidegenerate. Such quasidegeneracies recur as $\Delta$ advances by $2\pi$, corresponding to a periodicity in $l^2$ of $4\pi/\delta S$ (or two flux quanta). This periodicity is not affected by the additional phase $2\bar{\phi}$ in $\Delta$, because $\bar{\phi}$ varies on the scale  $2\pi/S_{\sma{\square}}$,\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary  $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$ [cf.\  Fig.\ 10 in 100page]. Moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$.[AALG]} which is much larger than $4\pi/\delta S$. To recapitulate, half the Landau-level quasi-crossings (over the $B$ axis) are destabilized  by tunneling; the robustness of the other half relies on $\mathfrak{c}_2$ symmetry. There exists a complementary argument for the existence of Landau-level quasi-crossings in the Klein-tunneling limit $(\tau{=}0)$ (cf. Fig. \ref{fig:Cn-breakdown}(c) upper panel): the two independent orbits are related by $\mathfrak{c}_2$ symmetry, leading to exactly-degenerate Landau levels.

@@

For our last illustration, we consider a II-Dirac model with $\mathfrak{c}_3$  symmetry, as   illustrated in Fig. \ref{fig:Cn-breakdown}(b). In the adiabatic regime ($\tau{\approx}1$), Landau-level quasidegeneracies occur with a periodicity of one flux quantum; however, in the Klein-tunneling regime ($\tau{\approx}0$), there exists only one dominant orbit shaped like a three-fold-symmetric trefoil knot (cf. Fig.\ref{fig:Cn-breakdown}(c) lower panel) --  all Landau levels are nondegenerate with spacing determined by the effective mass of the trefoil; this property generalizes to $\mathfrak{c}_N$-symmetric II-Dirac models with odd $N$.
